% Chapter Template

\chapter{Conclusion} % Main chapter title

\label{Chapter6} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Future work}

After all, there is still much work that can be done. The current version of the component is in beta version
because there are still some bugs that need to be solved. E.g., problems with destroying react child components
in a drop-down menu or hovering effect. These bugs do not affect the functionality nor visual site, but they are not handled properly and result in errors in console.

Next thing I am planning to look at, as I already mentioned earlier, is a better function for filtering and processing data. Current methods are the first thing that comes to my mind and definitely can be optimized.

Also, I could add more interface features that will make the component even more flexible. 

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Summary}

In conclusion, Intelligent tree select component is based on already great components such as \cite{react-select} and \cite{react-virtualized-select}. This component is providing functionality for displaying options as a tree or creating a new one. As well it can be used with linked data, support two data formats, multiple providers, and much more. A structure is divided into three parts that are independent of themselves. Performance is not perfect in current beta version, but it can perfectly handle a large number of options in acceptable time. Overall compared to other solutions this component is same in core functionality but better in other aspects.

%----------------------------------------------------------------------------------------